On the marginal value of swimming in woodland caribou

### 2021-04-12 paper/manuscript.Rmd
median > mean
new title

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author:
  - name: Quinn M.R. Webber
    institute: cabe
    correspondence: true
  - name: Jack G. Hendrix
    institute: cabe
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: ../references/swim.bib
csl: ecology.csl
---

@@

# Mean per individual
neventidMean <- round(mean(neventid$N))

>>>>

---
title: On the marginal value of swimming in woodland caribou
author:
  - name: Quinn M.R. Webber
    institute: cabe
    correspondence: true
  - name: Jack G. Hendrix
    institute: cabe
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: ../references/swim.bib
csl: ecology.csl
---

@@

# Mean per individual
neventidMedian <- round(median(neventid$N))
